Optimised Cost Considering Huffman Code for Biological Data Compression

### 2015-02-10 Article/Article.tex
modified for signal processing

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}
\journal{Computers \& Mathematics with Applications}
\bibliographystyle{elsarticle-num}
\begin{document}

@@

\begin{abstract}
%% Text of abstract
Classical Huffman code has widely been used to compress biological datasets. Though a considerable reduction of size of data is obtained by classical Huffman code, yet, more efficient encoding is possible by treating binary bits differently considering requirement of transmission time, energy consumption, and likewise. A number of techniques already modified Huffman code algorithm to  obtain optimal prefix-codes for unequal letter costs in order to reduce overall transmission cost (time). 
%In the recent year with the wide use of cloud and the distributed application in our life, the data transmission become more challenging over the years. 
In this paper we propose a new approach to improve compression performance of one such extension, cost considering approach (CCA),   %the data transmission technique by improving the representation of Huffman code with the use of a 
by applying genetic algorithm for optimal allocation of the codewords to the symbols. 
%The work in this research is consists of two steps. 
The approach start with generating a set of codewords for different input symbols based on their frequencies by considering cost (length) of 0 and 1 as $\alpha$ and $\beta$,~$\alpha < \beta$. This step ensures optimal cost encoding, however, compression performance is not higher than classical Huffman code. 
%The aim of the codes generation method is to minimise the number of ones on the generated codes, which minimise the cost of the transmission. 
%To improve compression performance, the second part of the approach uses genetic algorithm to find an optimal allocation of generated codes to different symbols. 
The idea is to sacrifice some cost to minimise total number of bits, hence, the genetic algorithm works by giving penalty on cost. The performance of the approach is evaluated by applying it to compress some standard biological datasets and comparing the result with the results produced by classical Huffman code and cost considering Huffman code.
% The case study of the approach is the biological data, which present a good application area to data compression with the huge growth of the biological data bases. 
%The results are very promising and we have compared with the standard cost considering Huffman code and the original Huffman code.
\end{abstract}

\begin{keyword}
Data Compression, Huffman code, Cost Considering Approach, Genetic algorithm, Biological data.
%% keywords here, in the form: keyword \sep keyword

>>>>

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}
\journal{Signal Processing}
\bibliographystyle{elsarticle-num}
\begin{document}

@@

\begin{abstract}
%% Text of abstract
Classical Huffman code has widely been used to compress biological datasets. Though a considerable reduction of size of data is obtained by classical Huffman code, yet, more efficient encoding is possible by treating binary bits differently considering requirement of transmission time, energy consumption, and likewise. A number of techniques already modified Huffman code algorithm to  obtain optimal prefix-codes for unequal letter costs in order to reduce overall transmission cost (time). 
%In the recent year with the wide use of cloud and the distributed application in our life, the data transmission become more challenging over the years. 
In this paper we propose a new approach to improve compression performance of one such extension, cost considering approach (CCA),   %the data transmission technique by improving the representation of Huffman code with the use of a 
by applying genetic algorithm for optimal allocation of the codewords to the symbols. 
%The work in this research is consists of two steps. 
%The approach start with generating a set of codewords for different input symbols based on their frequencies by considering cost (length) of 0 and 1 as $\alpha$ and $\beta$,~$\alpha < \beta$. This step ensures optimal cost encoding, however, compression performance is not higher than classical Huffman code. 
%The aim of the codes generation method is to minimise the number of ones on the generated codes, which minimise the cost of the transmission. 
%To improve compression performance, the second part of the approach uses genetic algorithm to find an optimal allocation of generated codes to different symbols. 
The idea is to sacrifice some cost to minimise the total number of bits, hence, the genetic algorithm works by giving penalty on the cost. The performance of the approach is evaluated by applying it to compress some standard biological datasets. The experiments yield that the proposed approach improves the compression performance of the CCA considerably without increasing the cost significantly.%     and comparing the result with the results produced by classical Huffman code and cost considering Huffman code.
% The case study of the approach is the biological data, which present a good application area to data compression with the huge growth of the biological data bases. 
%The results are very promising and we have compared with the standard cost considering Huffman code and the original Huffman code.
\end{abstract}

\begin{keyword}
Data Compression, Huffman Code, Genetic Algorithm, Cost Considering Approach, Signal Processing.
%% keywords here, in the form: keyword \sep keyword
